My Linux Notes

### 2018-10-11 Ubuntu_16.04_setup/mylinux.Rmd
up

@@

>>>>

#### pipe

```bash
[ -f <file-name> ] && <command>
[ -d <dir-name> ] || <command>
```

@@

String Manipulation
========

## cut

`list.txt`:
```
10/04 2018,xaringan
09/28 2018,pttR-intro
```

Read one line of `list.txt` in each loop,
cut the line into 2 fields, seperated by `,`.
```bash
while read p; do
  date=$(echo "$p" | cut -d ',' -f 1)
  file=$(echo "$p" | cut -d ',' -f 2)
done < list.txt
```

## printf

More consistent then `echo`, 
can use special characters like `\\n`.
```bash
printf "$date &nbsp;&nbsp; [$file](${file}/index.html)\n\n"
```

## cat

`cat` the text between the two `_EOF_`.
```bash
cat << _EOF_
---
title: Slides
---

# List of Slides
<br><br>
_EOF_
```

`cat` the text between the two `_EOF_`, then **redirect the text to `index.md`**.
```bash
cat >> index.md  << _EOF_
---
title: Slides
---

# List of Slides
<br><br>
_EOF_
```
